---
title: "p8105_hw1_akg2197"
author: "Annie Gorman"
date: "2024-09-20"
output: github_document
---
# Problem 0.1
```{r setup, include=FALSE}
library(tidyverse)
data("penguins", package = "palmerpenguins")
view(penguins)
```

# Problem 1
This dataset includes variables species ("species"), island ("island"), bill
length in mm ("bill_length_mm"), bill depth in mm ("bill_depth_mm"), flipper length in mm
("flipper_length_mm"), body mass in grams ("body_mass_g"), sex, and year. 

The rows of the dataset are `r nrow(penguins)` 
The columns of the dataset are `r ncol(penguins)`
The mean flipper length is `r mean(pull(penguins, flipper_length_mm), na.rm = TRUE)`

# Scatterplot of bill length vs. flipper length
```{r}
scatterplot <- ggplot(penguins, aes(
  x = bill_length_mm, 
  y = flipper_length_mm,
  color = species)) +
  geom_point()

ggsave("bill_vs_flipper.png", scatterplot)
```

# Problem 2
la_df = tibble(
  norm_samp = rnorm(10),
  norm_samp_pos = norm_samp > 0,
  b_vec = c("Q", "W", "E", "R", "T", "Y", "U", "I", "O", "P"),
  level = factor(c("low","low","low", "medium","medium","medium","medium", "high","high","high"))
)

mean(pull(la_df, norm_samp))
mean(pull(la_df, norm_samp_pos))
mean(pull(la_df, b_vec))
mean(pull(la_df, level))
```

We have an error in pulling the level variable and taking the mean of a character because 
it is non-numeric.
