---
title: "p8105_hw1_akg2197"
author: "Annie Gorman"
date: "2024-09-20"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
data("penguins", package = "palmerpenguins")
view(penguins)
```


Thus dataset includes variables species ("species"), island ("island"), bill
length in mm ("bill_length_mm")

The data in this dataset, including names / values of important variables
The rows of the dataset are `r nrow(penguins)` 
The columns of the dataset are `r ncol(penguins)`
The mean flipper length is `r mean(pull(penguins, flipper_length_mm), na.rm = TRUE)`

```{r ggplot, include=FALSE}
ggplot(weather_df, aes(x = tmin, y = tmax)) + 
  geom_point(aes(color = name))

# Problem 2
la_df = tibble(
  norm_samp = rnorm(10),
  norm_samp_pos = norm_samp > 0,
  b_vec = c("Q", "W", "E", "R", "T", "Y", "U", "I", "O", "P"),
  level = factor(c("low","low","low", "medium","medium","medium","medium", "high","high","high"))
)

mean(pull(la_df, norm_samp))
mean(pull(la_df, norm_samp_pos))
mean(pull(la_df, b_vec))
mean(pull(la_df, level))
```
We have an error in pulling the level variable and taking the mean of a character because 
it is non-numeric.
